---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library(noplyr)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis-CI Build Status](https://travis-ci.org/yonicd/noplyr.svg?branch=master)](https://travis-ci.org/yonicd/noplyr)
[![Codecov test coverage](https://codecov.io/gh/yonicd/noplyr/branch/master/graph/badge.svg)](https://codecov.io/gh/yonicd/noplyr?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Covrpage Summary](https://img.shields.io/badge/covrpage-Last_Build_2019_01_12-yellowgreen.svg)](http://tinyurl.com/y8wab3dk)

# noplyr

Run basic functions of `dplyr` and `tidyr` with only base `R` and `rlang`.

> Disclaimer: this is experimental, use deliberately and with caution.

## When could this package be useful?

  - Non DBI related data manipulations
  - Continuous integration `R` scripts
  - Low package dependency workflows or products

## Installation

```{r, eval=FALSE}
remotes::install_github('yonicd/noplyr')
```

## Current Build 

```{r}
data.frame(package = c('rlang','dplyr','tidyr'),
           stringsAsFactors = FALSE)%>%
  noplyr::group_by(package)%>%
  noplyr::mutate(version = as.character(packageVersion(package)))%>%
  knitr::kable()
```

### dplyr

  - arrange
  - count
  - filter
  - group_by
  - mutate 
  - rename
  - select
  - summarize

### tidyr

  - gather
  - spread
  - unite
  
### todo

  - do
  - joins
  - binds
  - separate

### Similar Packages

  - [freebase](https://github.com/hrbrmstr/freebase) : A ‘usethis’-esque Package for Base R Versions of ‘tidyverse’ Code

  - [tbltools](https://github.com/mkearney/tbltools): Tools for Working with Tibbles

### CoC
  
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
