---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library(bplyr)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis-CI Build Status](https://travis-ci.org/yonicd/bplyr.svg?branch=master)](https://travis-ci.org/yonicd/bplyr)
[![Codecov test coverage](https://codecov.io/gh/yonicd/bplyr/branch/master/graph/badge.svg)](https://codecov.io/gh/yonicd/bplyr?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Covrpage Summary](https://img.shields.io/badge/covrpage-Last_Build_2019_03_05-yellowgreen.svg)](http://tinyurl.com/y4cpzsxq)

# base + plyr = bplyr

Run basic functions of `dplyr` and `tidyr` with only base `R` and `rlang`.

> Disclaimer: this is experimental, use deliberately and with caution.

> Previously called noplyr

## When could this package be useful?

  - Non DBI related data manipulations
  - Continuous integration `R` scripts
  - Low package dependency workflows or products

All functions in bplyr mimic specific functions in dplyr and tidyr, and have a trailing prefix b_* to them. so arrange is b_arrange and so forth. 

This has been done as to not create namespace conflicts with dplyr or tidyr, as this package does not try to replace the intended full features of those packages, but create light weight, fast installing alternatives when applicable. 

## Installation

```{r, eval=FALSE}
remotes::install_github('yonicd/bplyr')
```

## Current Build 

```{r}
data.frame(package = c('rlang','dplyr','tidyr'),
           stringsAsFactors = FALSE)%>%
  bplyr::b_group_by(package)%>%
  bplyr::b_mutate(version = as.character(packageVersion(package)))%>%
  knitr::kable()
```

### dplyr

  - arrange
  - count
  - filter
  - group_by
  - mutate 
  - rename
  - select
  - summarize

### tidyr

  - gather
  - spread
  - unite
  
### todo

  - do
  - joins
  - binds
  - separate

### Similar Packages

  - [freebase](https://github.com/hrbrmstr/freebase) : A ‘usethis’-esque Package for Base R Versions of ‘tidyverse’ Code

  - [tbltools](https://github.com/mkearney/tbltools): Tools for Working with Tibbles

### CoC
  
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
